Localization properties, observable character and computational reliability of the linear response in open systems

### 2018-07-09 AnalyticStructure_main.tex
Update on Overleaf.

\section{Conclusions and Perspectives}
In the analysis presented in this paper we have investigated how 
computational results of linear-response calculations of molecular systems 
might be compared among various formalisms.
In particular, we have been interested in identifying the quantities that can
be expressed in computational setups that are originally conceived for 
\emph{localised} objects, which are the \emph{only} quantities that
play a significant role in GS calculations.

We have shown that all response densities for $\omega$ above the first IP
\emph{have} to be expressed in terms of genuinely delocalized states, whereas below this threshold,
under reasonable assumptions on the perturbing operators,
the perturbed density operator is genuinely localized.
In this localized regime, it is possible to achieve convergence of the numerical result
by increasing the completeness of the basis with the usual GS rationales.
One might expect that more complete basis will give more precise results, regardless of their asymptotic behavior.
A comparison among various codes in view of reproducibility should therefore be performed 
initially in this regime.

>>>>

\section{Conclusions and Perspectives}
% In the analysis presented in this paper we have investigated how 
% computational results of linear-response calculations of molecular systems 
% might be compared among various formalisms.
% In particular, we have been interested in identifying the quantities that can
% be expressed in computational setups that are originally conceived for 
% \emph{localised} objects, which are the \emph{only} quantities that
% play a significant role in GS calculations.

By analysing the fundamental equations of LR calculations of molecules, we have shown that the response density for values of $\omega$ above the first IP
\emph{have} to be expressed in terms of genuinely delocalized states. %, whereas 
Below this threshold,
under reasonable assumptions on the perturbing operators,
the perturbed density operator is genuinely localized.
In this localized regime, it is possible to achieve convergence of the numerical result
by increasing the completeness of the basis with the usual GS rationales.
One might expect that more complete basis will give more precise results, regardless of their asymptotic behavior.
A comparison among various codes in view of reproducibility should therefore be performed 
initially in this regime.
